Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-07-10 manuscripts/manuscript1.qmd
update quarto

predictions(models$"Neurosurgical Intervention", by = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous(
    limits = c(0,100)
  ) +
  scale_x_continuous(
    limits = c(0, 0.14),
    breaks = seq(0, 0.14, 0.02),
    labels = scales::percent
  ) +
  labs(
    title = "Predicted Probability",
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()

>>>>

predictions(models$"Neurosurgical Intervention", by = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous(
    limits = c(0, 100)
  ) +
  scale_x_continuous(
    limits = c(0, 0.14),
    breaks = seq(0, 0.14, 0.02),
    labels = scales::percent
  ) +
  labs(
    title = "Predicted Probability",
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()
